Q1: Are lake and terrestrial primary productivity coherent?

### 2019-04-18 AnalysisCode/ms1_analyses.Rmd
continued code development

@@

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, tsvars=c("chla"), minmos=3, minobs=3)
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #69 lakes here

>>>>

This document organizes for openness and reproducibility analyses of the temporal coherence of interannual variation in lake primary productivity with terrestrial primary productivity in the landscape surrounding the lake.

@@

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, tsvars=c("chla"), minmos=3, minobs=3)
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #73 lakes here
